### 2012-11-25 paper.tex
minor change: changed todos to inline todos to avoid latex warnings
added picture with crappy entry

\usepackage{float}
\usepackage{placeins}
\usepackage{natbib}
% philipp: added for code listings
\usepackage{listings}
\usepackage{booktabs}
\usepackage{morefloats}
\bibliographystyle{plain}

@@

\paragraph{}The last preprocessing step was the replacement of missing values (data imputation). Most of the data was complete but there were still some data records having missing values which we replaced by the mean values of the specific variables. One data record did contain completeley useless data and was thus removed (see at the picture below).

@@

\todo{Compare results with/without preprocessing}

\subsection{Decision Tree}
\todo{robert: do you want to keep this section? on the one hand it shows what happens if we run a desicion tree with attributes on which the the prediction attribute depends, but on the other hand we know we should not do that. please decide. i'm ok with both (philipp)}
%------------------------------------------------
On the first glimpse, it is an easy task for a decision based algorithm:

>>>>

\usepackage{color}
\usepackage{float}
\usepackage{placeins}
\usepackage{natbib}
% philipp: added for code listings
\usepackage{listings}
\lstset{
    captionpos=b
}
\newcommand{\Hilight}{\makebox[0pt][l]{\color{red}\rule[-4pt]{0.65\linewidth}{14pt}}}
\usepackage{booktabs}
\usepackage{morefloats}
\bibliographystyle{plain}

@@

\paragraph{}The last preprocessing step was the replacement of missing values (data imputation). Most of the data was complete but there were still some data records having missing values which we replaced by the mean values of the specific variables. One data record did contain completeley useless data and was thus removed (see at in listing \ref{lst:crappy-entry}).

\begin{lstlisting}[escapechar=\%, float=htb, caption={76 years old patient without useful information}, label=lst:crappy-entry]
20,1,59,0,0.030,21.300,6.290,17,1.310,0.928,name,2,0
0.25,1,63,1,?,?,?,23,2.300,0.714,name,2,1
%\Hilight% ?,?,?,77,?,?,?,?,?,2,?,name,2,?
2,1,56,1,0.040,14,5,?,?,?,name,2,1
7,1,61,1,0.270,?,?,9,1.500,0.428,name,2,1
\end{lstlisting}

@@

\todo[inline]{Compare results with/without preprocessing}

\subsection{Decision Tree}
\todo[inline]{robert: do you want to keep this section? on the one hand it shows what happens if we run a desicion tree with attributes on which the the prediction attribute depends, but on the other hand we know we should not do that. please decide. i'm ok with both (philipp)}
%------------------------------------------------
On the first glimpse, it is an easy task for a decision based algorithm:
